Old or Heavy?\\Decaying Gracefully with Age/Weight Shapes.

### 2019-02-28 papers/CADE19/paper.tex
more figures

\begin{table}[t]
	\caption{
The mean relative performance drop (in terms of activations compared to an optimal value) choosing a single AWR over an entire problem set causes.
The percentage of problems in this set solved by the AWR setting is also shown.
No setting is significantly ``better'' or ``worse'' than the others, but some have more variance in performance.
A ratio of 1:4 produces an unusually well-behaved maximum performance drop.
\sandm~found that 1:5 had a similar property, but this might be explained by differences in test environment.
}
	\centering
	\begin{tabular}{l | c | c | c  c }
		AWR & \% Solved & Maximum Drop & Mean Drop & (Standard Deviation)\\
\hline
8:1 & 85.25 & 150.67 & 1.37 & 1.98\\
5:1 & 86.10 & 122.22 & 1.33 & 1.64\\
4:1 & 86.93 & 101.44 & 1.32 & 1.42\\
3:1 & 87.63 & 105.00 & 1.29 & 1.41\\
2:1 & 88.62 & 112.67 & 1.27 & 1.45\\
3:2 & 89.83 & 119.89 & 1.27 & 1.51\\
5:4 & 89.98 & 125.00 & 1.26 & 1.55\\
1   & 90.56 & 133.56 & 1.26 & 1.63\\
2:3 & 91.20 & 147.67 & 1.28 & 1.79\\
2   & 91.68 & 162.67 & 1.31 & 1.97\\
3   & 91.81 & 190.56 & 1.37 & 2.30\\
4   & 91.85 & 17.41 & 1.38 & 0.67\\
5   & 92.00 & 133.67 & 1.44 & 1.70\\
6   & 91.57 & 106.44 & 1.47 & 1.46\\
7   & 91.49 & 104.89 & 1.49 & 1.44\\
8   & 91.09 & 101.33 & 1.53 & 1.45\\
10  & 90.52 & 101.78 & 1.60 & 1.53\\
12  & 90.00 & 101.67 & 1.65 & 1.62\\
14  & 89.29 & 103.00 & 1.70 & 1.75\\
16  & 89.42 & 101.33 & 1.74 & 1.76\\
20  & 88.61 & 100.89 & 1.82 & 1.94\\
24  & 88.26 & 101.33 & 1.89 & 2.08\\
28  & 87.57 & 99.22 & 1.96 & 2.24\\
32  & 87.01 & 100.00 & 1.99 & 2.36\\
40  & 86.23 & 98.78 & 2.09 & 2.64\\
50  & 84.93 & 98.78 & 2.17 & 2.88\\
64  & 84.17 & 101.22 & 2.28 & 3.19\\
128 & 81.34 & 107.44 & 2.57 & 4.16\\
1024 & 73.11 & 222.01 & 2.83 & 7.55
	\end{tabular}

	\label{tab:no-best-awr}
\end{table}

\begin{table}
	\caption{Relative performance gain, showing the ratio in activations between the best AWR setting for a given problem and another base setting. We compare the base settings of 1:1 (Vampire's default), 1:5 (the best-behaved from \sandm), and the worst setting for the problem.}
	\centering
	\begin{tabular}{c | c | c c}
		& Maximum Gain & Mean Gain & (Standard Deviation)\\
		\hline
		1:1 & 133.56 & 1.26 & 1.63 \\
		1:5 & 133.67 & 1.44 & 1.70 \\
		(worst) & 222.01 & 3.95 & 7.60 \\
	\end{tabular}
	\label{tab:awr-improvement}
\end{table}

@@

\begin{table}
	\caption{
Results for the tested configurations.
\emph{Proved} refers to the total number of problems a configuration solved.
\emph{Fresh} is the number of problems a configuration solved which were not solved by the baseline.
\emph{Uniques} is the number of problems a configuration solved which were not solved by any other configuration.
\emph{\(u\)-score} is a refined unique score which correlates to a configuration's utility in solving new problems, as used in Hoder \emph{et al.}~\cite{u-score}.
	}
	\centering
	\begin{tabular}{l l l l l l}
		Configuration & Frequency & Proved & Fresh & Uniques & \(u\)-score\\
		\hline
		baseline & -- & 13057 & 0 & 1 & 714.2\\
		converge & 1 & 13039 & 24 & 3 & 714.3\\
		converge & 5 & 13029 & 27 & 1 & 709.5\\
		converge & 10 & 13028 & 35 & 5 & 714.3\\
		converge & 50 & 13015 & 45 & 5 & 712.8\\
		converge & 100 & 12976 & 51 & 1 & 705.9\\
		converge & 500 & 12895 & 63 & 4 & 698.3\\
		converge & 1000 & 12837 & 52 & 0 & 688.6\\
		converge & 5000 & 12775 & 53 & 1 & 682.4\\
		converge & 10000 & 12751 & 53 & 0 & 678.7\\
		decay & 1 & 12698 & 48 & 1 & 673.6\\
		decay & 5 & 12702 & 51 & 1 & 674.9\\
		decay & 10 & 12698 & 48 & 1 & 674.2\\
		decay & 50 & 12712 & 49 & 2 & 679.1\\
		decay & 100 & 12726 & 46 & 1 & 678.8\\
		decay & 500 & 12795 & 29 & 1 & 685.5\\
		decay & 1000 & 12860 & 29 & 2 & 692.6\\
		decay & 5000 & 12982 & 16 & 2 & 707.1\\
		decay & 10000 & 13002 & 7 & 0 & 706.3\\
		\hline
		converge & (combined) & 13167 & 117 & -- & --\\
		decay & (combined) & 13106 & 93 & -- & --\\
	\end{tabular}
	\label{tab:results}
\end{table}

>>>>

\begin{table}[t]
	\caption{
The mean relative performance drop (in terms of activations compared to an optimal value) choosing a single AWR over the problem set (approx. 8,000 problems solved in 1 second) causes.
The percentage of problems in this set solved by the AWR setting is also shown.
No setting is significantly ``better'' or ``worse'' than the others, but some have more variance in performance.
A ratio of 1:4 produces an unusually well-behaved maximum performance drop.
\sandm~found that 1:5 had a similar property, but this might be explained by differences in prover and test environment.
}
	\centering
	\begin{tabular}{l | c | c | c | c  c }
		AWR & \% Solved & Uniques & Maximum Drop & Mean Drop & (Standard Deviation)\\
\hline
8:1 & 85.25 & 16 & 150.67 & 1.37 & 1.98\\
5:1 & 86.10 & 1 & 122.22 & 1.33 & 1.64\\
4:1 & 86.93 & 1 & 101.44 & 1.32 & 1.42\\
3:1 & 87.63 & 2 & 105.00 & 1.29 & 1.41\\
2:1 & 88.62 & 3 & 112.67 & 1.27 & 1.45\\
3:2 & 89.83 & 2 & 119.89 & 1.27 & 1.51\\
5:4 & 89.98 & 4 & 125.00 & 1.26 & 1.55\\
1   & 90.56 & 4 & 133.56 & 1.26 & 1.63\\
2:3 & 91.20 & 9 & 147.67 & 1.28 & 1.79\\
2   & 91.68 & 0 & 162.67 & 1.31 & 1.97\\
3   & 91.81 & 5 & 190.56 & 1.37 & 2.30\\
4   & 91.85 & 3 & \textbf{17.41} & 1.38 & 0.67\\
5   & 92.00 & 2 & 133.67 & 1.44 & 1.70\\
6   & 91.57 & 1 & 106.44 & 1.47 & 1.46\\
7   & 91.49 & 1 & 104.89 & 1.49 & 1.44\\
8   & 91.09 & 2 & 101.33 & 1.53 & 1.45\\
10  & 90.52 & 1 & 101.78 & 1.60 & 1.53\\
12  & 90.00 & 0 & 101.67 & 1.65 & 1.62\\
14  & 89.29 & 4 & 103.00 & 1.70 & 1.75\\
16  & 89.42 & 5 & 101.33 & 1.74 & 1.76\\
20  & 88.61 & 3 & 100.89 & 1.82 & 1.94\\
24  & 88.26 & 2 & 101.33 & 1.89 & 2.08\\
28  & 87.57 & 2 & 99.22 & 1.96 & 2.24\\
32  & 87.01 & 1 & 100.00 & 1.99 & 2.36\\
40  & 86.23 & 4 & 98.78 & 2.09 & 2.64\\
50  & 84.93 & 1 & 98.78 & 2.17 & 2.88\\
64  & 84.17 & 2 & 101.22 & 2.28 & 3.19\\
128 & 81.34 & 3 & 107.44 & 2.57 & 4.16\\
1024 & 73.11 & 23 & 222.01 & 2.83 & 7.55
	\end{tabular}
	\label{tab:no-best-awr}
\end{table}

\begin{table}
	\caption{
Relative performance gain, showing the ratio in activations between the best AWR setting for a given problem and another base setting.
We compare the base settings of 1:1 (Vampire's default), 1:5 (the best-behaved from \sandm), and the worst setting for the problem.
Where the problem is not solved at all by the base setting, it is ignored.
}
	\centering
	\begin{tabular}{c | c | c c}
		& Maximum Gain & Mean Gain & (Standard Deviation)\\
		\hline
		1:1 & 133.56 & 1.26 & 1.63 \\
		1:5 & 133.67 & 1.44 & 1.70 \\
		(worst) & 222.01 & 3.95 & 7.60 \\
	\end{tabular}
	\label{tab:awr-improvement}
\end{table}

@@

\begin{table}
	\caption{
Results for the tested configurations.
\emph{Proved} refers to the total number of problems a configuration solved.
\emph{Fresh} is the number of problems a configuration solved which were not solved by the baseline.
\emph{Uniques} is the number of problems a configuration solved which were not solved by any other configuration.
\emph{\(u\)-score} is a refined unique score which correlates to a configuration's utility in solving new problems, as used in Hoder \emph{et al.}~\cite{u-score}.
	}
	\centering
	\begin{tabular}{l l l l l l}
		Configuration & Frequency & Proved & Fresh & Uniques & \(u\)-score\\
		\hline
		baseline & -- & 13057 & 0 & 1 & 714.2\\
		converge & 1 & 13039 & 24 & 3 & 714.3\\
		converge & 5 & 13029 & 27 & 1 & 709.5\\
		converge & 10 & 13028 & 35 & 5 & 714.3\\
		converge & 50 & 13015 & 45 & 5 & 712.8\\
		converge & 100 & 12976 & 51 & 1 & 705.9\\
		converge & 500 & 12895 & 63 & 4 & 698.3\\
		converge & 1000 & 12837 & 52 & 0 & 688.6\\
		converge & 5000 & 12775 & 53 & 1 & 682.4\\
		converge & 10000 & 12751 & 53 & 0 & 678.7\\
		decay & 1 & 12698 & 48 & 1 & 673.6\\
		decay & 5 & 12702 & 51 & 1 & 674.9\\
		decay & 10 & 12698 & 48 & 1 & 674.2\\
		decay & 50 & 12712 & 49 & 2 & 679.1\\
		decay & 100 & 12726 & 46 & 1 & 678.8\\
		decay & 500 & 12795 & 29 & 1 & 685.5\\
		decay & 1000 & 12860 & 29 & 2 & 692.6\\
		decay & 5000 & 12982 & 16 & 2 & 707.1\\
		decay & 10000 & 13002 & 7 & 0 & 706.3\\
		\hline
		converge & (combined) & 13167 & 117 & 41 & --\\
		decay & (combined) & 13106 & 93 & 17 & --\\
	\end{tabular}
	\label{tab:results}
\end{table}
